Glycolysis Network

### 2024-09-27 RussoPaper/RussoClimbingPlots.Rmd
Dina Folder Update

---
title: "Russo Manuscript Climbing Plot"
author: "John Santiago"
date: "2024-03-29"
output: pdf_document
---

@@

@@

fig4ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 4AB Climbing Data ok371 cha gbb climbing cm_sec.csv", header = T)

@@

@@

```{r echo = F}

@@

```{r echo = F}

norm.female = na.omit(female)
norm.female$normval = 0
i=1
while(i <= nrow(norm.female)){
  norm.female$normval[i] = norm.female$corrected.values[i]/
    fmean$mean[fmean$geno == 'silent' & fmean$day == norm.female$day[i]]
  i = i +1
}

@@

```{r echo = F, fig.height=10}

@@

```{r echo = F}

>>>>

---
title: "Russo Manuscript Climbing Plot"
author: "John Santiago"
date: "2024-03-29"
output: html_document
---

@@

```{r include = F, echo = F, include = F}

fig2ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 2AB.csv", header = T)
fig2ab$Sample = paste(fig2ab$Genotype, paste(fig2ab$Sex, fig2ab$Day))

mean.fig2 = rep(0, length(unique(fig2ab$Sample)))
names(mean.fig2) = unique(fig2ab$Sample)
var.fig2 = mean.fig2

i=1
while(i<=length(mean.fig2)){
  mean.fig2[i] = mean(as.numeric(na.omit(fig2ab[fig2ab$Sample == names(mean.fig2)[i], 'Rate'])))

    var.fig2[i] = var(as.numeric(na.omit(fig2ab[fig2ab$Sample == names(mean.fig2)[i], 'Rate'])))

eb = data.frame(sample = names(mean.fig2),
                y0 = mean.fig2 - var.fig2,
                y1 = mean.fig2 + var.fig2)

f.fig2ab = fig2ab[fig2ab$Sex == 'F' &
                  (fig2ab$Day == 3 |
                  fig2ab$Day == 28 |
                  fig2ab$Day == 35) &
                  fig2ab$Genotype != 'w1118',]

f.fig2ab = f.fig2ab[order(fig2ab$Day),]
f.fig2ab$Sample = paste(f.fig2ab$Genotype, f.fig2ab$Day)
f.fig2ab$Sample = factor(f.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
                                                     'dSodWT 28', 'A4V 28',
                                                     'dSodWT 35', 'A4V 35'))
f.fig2ab = na.omit(f.fig2ab)
f.fig2ab$x = as.numeric(f.fig2ab$Sample)
f.fig2ab$x[f.fig2ab$x > 4] = f.fig2ab$x[f.fig2ab$x > 4] + 1
f.fig2ab$x[f.fig2ab$x > 2] = f.fig2ab$x[f.fig2ab$x > 2] + 1
f.fig2ab$color = 'brown'
f.fig2ab$color[f.fig2ab$Genotype == 'dSodWT'] = 'steelblue'
f.fig2ab = f.fig2ab[order(f.fig2ab$Rate),]
f.fig2ab = f.fig2ab[order(f.fig2ab$Sample),]
f.fig2ab$x.adj = rep(c(-.25, .25 ,0), 12)
f.fig2ab$x.adj = c(0, -.15, .15, -.1, .1, 0,
                   0, -.1, .1, -.1, .1, 0,

                   -.15, .15, 0, 0, 0, 0,
                   -.15, .15, 0, 0, 0, 0,

                   -.15, .15, 0, -.15, .15, 0,
                   -.15, .15, 0, -.15, .15, 0)

f.fig2ab$x = f.fig2ab$x + f.fig2ab$x.adj

par(mar=c(5.1, 4.1, 4.1, 5.6))

boxplot(f.fig2ab$Rate~f.fig2ab$Sample,
        at = c(1,2, 4,5, 7,8),
        xaxt = 'none',
        xlab = "Day",
        ylab = 'Veloxicty (cm/sec)',
        main = "Female Climbing Velocity")
points(x = f.fig2ab$x,
       y = f.fig2ab$Rate,
       pch = 21,
       bg = f.fig2ab$color)
axis(side = 1,
     at = c(1.5, 4.5, 7.5),
     labels = c(3, 28,35))

legend('topright',
       inset=c(-0.175,0),
       legend = c('Silent', 'A4V'), 
       fill = c('steelblue', 'brown'),
       cex = .65,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

m.fig2ab = fig2ab[fig2ab$Sex == 'M' &
                  (fig2ab$Day == 3 |
                  fig2ab$Day == 10 |
                  fig2ab$Day == 16) &
                  fig2ab$Genotype != 'w1118',]

m.fig2ab = m.fig2ab[order(fig2ab$Day),]
m.fig2ab$Sample = paste(m.fig2ab$Genotype, m.fig2ab$Day)
m.fig2ab$Sample = factor(m.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
                                                     'dSodWT 10', 'A4V 10',
                                                     'dSodWT 16', 'A4V 16'))
m.fig2ab = na.omit(m.fig2ab)
m.fig2ab$x = as.numeric(m.fig2ab$Sample)
m.fig2ab$x[m.fig2ab$x > 4] = m.fig2ab$x[m.fig2ab$x > 4] + 1
m.fig2ab$x[m.fig2ab$x > 2] = m.fig2ab$x[m.fig2ab$x > 2] + 1
m.fig2ab$color = 'brown'
m.fig2ab$color[m.fig2ab$Genotype == 'dSodWT'] = 'steelblue'

m.fig2ab = m.fig2ab[order(m.fig2ab$Rate),]
m.fig2ab = m.fig2ab[order(m.fig2ab$Sample),]
m.fig2ab$x.adj = rep(c(-.25, .25 ,0), 12)
m.fig2ab$x.adj = c(0, -.25, 0, .25, .15, 0,
                   0, -.25, 0, .25, -.15, .15,

                   0, 0, 0, -.1, .1, 0,
                   0, 0, -.1, .1, -.1, .1,

                   0, 0, 0, 0, 0, 0,
                   0, -.25, .25, 0, 0, 0)

m.fig2ab$x = m.fig2ab$x + m.fig2ab$x.adj

par(mar=c(5.1, 4.1, 4.1, 5.6))

boxplot(m.fig2ab$Rate~m.fig2ab$Sample,
        at = c(1,2, 4,5, 7,8),
        xaxt = 'none',
        xlab = "Day",
        ylab = 'Veloxicty (cm/sec)',
        main = "Male Climbing Velocity")
points(x = m.fig2ab$x,
       y = m.fig2ab$Rate,
       pch = 21,
       bg = m.fig2ab$color)
axis(side = 1,
     at = c(1.5, 4.5, 7.5),
     labels = c(3, 10, 16))

legend('topright',
       inset=c(-0.175,0),
       legend = c('Silent', 'A4V'), 
       fill = c('steelblue', 'brown'),
       cex = .65,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

f.fig2ab = fig2ab[fig2ab$Sex == 'F' &
                 (fig2ab$Day == 3 |
                  fig2ab$Day == 14 |
                  fig2ab$Day == 24 |
                  fig2ab$Day == 35) &
                  fig2ab$Genotype != 'w1118',]

f.fig2ab = f.fig2ab[order(fig2ab$Day),]
f.fig2ab$Sample = paste(f.fig2ab$Genotype, f.fig2ab$Day)
f.fig2ab$Sample = factor(f.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
                                                     'dSodWT 14', 'A4V 14',
                                                     'dSodWT 24', 'A4V 24',
                                                     'dSodWT 35', 'A4V 35'))
f.fig2ab = na.omit(f.fig2ab)
f.fig2ab$x = as.numeric(f.fig2ab$Sample)
f.fig2ab$x[f.fig2ab$x > 6] = f.fig2ab$x[f.fig2ab$x > 6] + 1
f.fig2ab$x[f.fig2ab$x > 4] = f.fig2ab$x[f.fig2ab$x > 4] + 1
f.fig2ab$x[f.fig2ab$x > 2] = f.fig2ab$x[f.fig2ab$x > 2] + 1
f.fig2ab$color = 'brown'
f.fig2ab$color[f.fig2ab$Genotype == 'dSodWT'] = 'steelblue'
f.fig2ab = f.fig2ab[order(f.fig2ab$Rate),]
f.fig2ab = f.fig2ab[order(f.fig2ab$Sample),]
f.fig2ab$x.adj = rep(c(-.25, .25 ,0), 16)
f.fig2ab$x.adj = c(0, -.25, .25, -.15, .15, 0,
                   0, -.15, .15, -.15, .15, 0,

                   0, 0, .2, -.2, 0, 0,
                   -.15, .15, 0, 0, -.15, .15,

                   0, 0, -.15, .15, 0, 0,
                   0, .2, -.2, 0, -.15, .15,

                   0, -.25, .25, -.15, .15, 0,
                   -.25, .25, 0, -.25, .25, 0)

f.fig2ab$x = f.fig2ab$x + f.fig2ab$x.adj

par(mar=c(5.1, 4.1, 4.1, 5.6))

boxplot(f.fig2ab$Rate~f.fig2ab$Sample,
        at = c(1,2, 4,5, 7,8, 10,11),
        xaxt = 'none',
        xlab = "Day",
        ylab = 'Veloxicty (cm/sec)',
        main = "Female Climbing Velocity")
points(x = f.fig2ab$x,
       y = f.fig2ab$Rate,
       pch = 21,
       bg = f.fig2ab$color)
axis(side = 1,
     at = c(1.5, 4.5, 7.5, 10.5),
     labels = c(3, 14, 24, 35))

legend('topright',
       inset=c(-0.175,0),
       legend = c('Silent', 'A4V'), 
       fill = c('steelblue', 'brown'),
       cex = .65,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

```{r echo = F, fig.width=7.5}

f.fig2ab = fig2ab[fig2ab$Sex == 'F' &
                 (fig2ab$Day == 3 |
                  fig2ab$Day == 14 |
                  fig2ab$Day == 20 |
                  fig2ab$Day == 28 |
                  fig2ab$Day == 35) &
                  fig2ab$Genotype != 'w1118',]

f.fig2ab = f.fig2ab[order(fig2ab$Day),]
f.fig2ab$Sample = paste(f.fig2ab$Genotype, f.fig2ab$Day)
f.fig2ab$Sample = factor(f.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
                                                     'dSodWT 14', 'A4V 14',
                                                     'dSodWT 20', 'A4V 20',
                                                     'dSodWT 28', 'A4V 28',
                                                     'dSodWT 35', 'A4V 35'))
f.fig2ab = na.omit(f.fig2ab)
f.fig2ab$x = as.numeric(f.fig2ab$Sample)
f.fig2ab$x[f.fig2ab$x > 8] = f.fig2ab$x[f.fig2ab$x > 8] + 1
f.fig2ab$x[f.fig2ab$x > 6] = f.fig2ab$x[f.fig2ab$x > 6] + 1
f.fig2ab$x[f.fig2ab$x > 4] = f.fig2ab$x[f.fig2ab$x > 4] + 1
f.fig2ab$x[f.fig2ab$x > 2] = f.fig2ab$x[f.fig2ab$x > 2] + 1
f.fig2ab$color = 'brown'
f.fig2ab$color[f.fig2ab$Genotype == 'dSodWT'] = 'steelblue'
f.fig2ab = f.fig2ab[order(f.fig2ab$Rate),]
f.fig2ab = f.fig2ab[order(f.fig2ab$Sample),]
f.fig2ab$x.adj = rep(c(-.25, .25 ,0), 20)
f.fig2ab$x.adj = c(0, -.25, .25, -.15, .15, 0,
                   0, -.15, .15, -.15, .15, 0,

                   0, 0, .2, -.2, 0, 0,
                   -.15, .15, 0, 0, -.15, .15,

                   0, 0, -.15, .15, 0, 0,
                   0, 0, -.25, .25, 0, 0,

                   0, -.25, .25, 0, 0, 0,
                   -.15, .15, 0, 0, 0, 0,

                   0, -.25, .25, -.15, .15, 0,
                   -.25, .25, 0, -.25, .25, 0)

f.fig2ab$x = f.fig2ab$x + f.fig2ab$x.adj

par(mar=c(5.1, 4.1, 4.1, 5.6))

boxplot(f.fig2ab$Rate~f.fig2ab$Sample,
        at = c(1,2, 4,5, 7,8, 10,11, 13,14),
        xaxt = 'none',
        xlab = "Day",
        ylab = 'Veloxicty (cm/sec)',
        main = "Female Climbing Velocity")
points(x = f.fig2ab$x,
       y = f.fig2ab$Rate,
       pch = 21,
       bg = f.fig2ab$color)
axis(side = 1,
     at = c(1.5, 4.5, 7.5, 10.5, 13.5),
     labels = c(3, 14, 20, 28, 35))

legend('topright',
       inset=c(-0.175,0),
       legend = c('Silent', 'A4V'), 
       fill = c('steelblue', 'brown'),
       cex = 1,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

```{r echo = F, fig.width=7.5}

m.fig2ab = fig2ab[fig2ab$Sex == 'M' &
                 (fig2ab$Day == 3 |
                  fig2ab$Day == 7 |
                  fig2ab$Day == 12 |
                  fig2ab$Day == 16) &
                  fig2ab$Genotype != 'w1118',]

m.fig2ab = m.fig2ab[order(fig2ab$Day),]
m.fig2ab$Sample = paste(m.fig2ab$Genotype, m.fig2ab$Day)
m.fig2ab$Sample = factor(m.fig2ab$Sample, levels = c('dSodWT 3', 'A4V 3',
                                                     'dSodWT 7', 'A4V 7',
                                                     'dSodWT 12', 'A4V 12',
                                                     'dSodWT 16', 'A4V 16'))
m.fig2ab = na.omit(m.fig2ab)
m.fig2ab$x = as.numeric(m.fig2ab$Sample)
m.fig2ab$x[m.fig2ab$x > 6] = m.fig2ab$x[m.fig2ab$x > 6] + 1
m.fig2ab$x[m.fig2ab$x > 4] = m.fig2ab$x[m.fig2ab$x > 4] + 1
m.fig2ab$x[m.fig2ab$x > 2] = m.fig2ab$x[m.fig2ab$x > 2] + 1
m.fig2ab$color = 'brown'
m.fig2ab$color[m.fig2ab$Genotype == 'dSodWT'] = 'steelblue'

m.fig2ab = m.fig2ab[order(m.fig2ab$Rate),]
m.fig2ab = m.fig2ab[order(m.fig2ab$Sample),]
m.fig2ab$x.adj = rep(c(-.25, .25 ,0), 16)
m.fig2ab$x.adj = c(0, -.25, .25, 0, -.1, .1,
                   0, -.25, .25, .0, -.1, .1,

                   0, 0, -.1, .1, 0, 0,
                   0, -.1, .1, 0, 0, 0,

                   0, -.1, .1, 0, 0, 0,
                   0, -.1, .1, 0, -.1, .1,

                   0, -.25, 0, .25, .15, 0,
                   0, -.25, 0, .25, -.15, .15)

m.fig2ab$x = m.fig2ab$x + m.fig2ab$x.adj

par(mar=c(5.1, 4.1, 4.1, 5.6))

boxplot(m.fig2ab$Rate~m.fig2ab$Sample,
        at = c(1,2, 4,5, 7,8, 10,11),
        xaxt = 'none',
        xlab = "Day",
        ylab = 'Veloxicty (cm/sec)',
        main = "Male Climbing Velocity")
points(x = m.fig2ab$x,
       y = m.fig2ab$Rate,
       pch = 21,
       bg = m.fig2ab$color)
axis(side = 1,
     at = c(1.5, 4.5, 7.5, 10.5),
     labels = c(3, 7, 12, 16))

legend('topright',
       inset=c(-0.175,0),
       legend = c('Silent', 'A4V'), 
       fill = c('steelblue', 'brown'),
       cex = 1,
       bty = 'n',
       pt.cex = .5,
       xpd = T)

@@

fig4ab = read.csv("/Users/johncsantiago/Documents/GitHub/WhartonLab/RussoPaper/Figure 4AB.csv", header = T)

@@

m.con = na.omit(male[male$geno == 'silent' | male$geno == 'A4V',])
m.cha = na.omit(male[grep('cha', male$geno),])

mallcha = rbind(m.con, m.cha)
mallcha$sample = paste0(mallcha$geno, mallcha$day)

mcha.mean = unique(mallcha[,c('geno', 'day')])
mcha.mean$sample = paste0(mcha.mean$geno, mcha.mean$day)
mcha.mean$mean = 0

i=1
while(i<=nrow(mcha.mean)){
  mcha.mean$mean[i] = mean(mallcha[mallcha$sample == mcha.mean$sample[i], 'corrected.values'])
  i = i+1
}

mcha.mean = mcha.mean[order(mcha.mean$day),]

f.fig4a = fig4ab[grep('f', fig4ab$vial_ID),]
f.fig4a = f.fig4a[f.fig4a$day == 6 |
                  f.fig4a$day == 13 |
                  #f.fig4a$day == 19 |
                  f.fig4a$day == 27,]

f.fig4a$Sample = paste(f.fig4a$geno, f.fig4a$day)
f.fig4a$geno = factor(f.fig4a$geno, levels = c("silent", 'silentcha', 'silentok',
                                               'A4V', 'A4Vcha', 'A4Vok'))

f.fig4a = f.fig4a[order(f.fig4a$day),]
f.fig4a = f.fig4a[order(f.fig4a$geno),]
f.fig4a$Sample = factor(f.fig4a$Sample, levels = unique(f.fig4a$Sample))

f.fig4a = na.omit(f.fig4a)
f.fig4a$x = as.numeric(f.fig4a$Sample)
f.fig4a$x[f.fig4a$x > 15] = f.fig4a$x[f.fig4a$x > 15] + 1
f.fig4a$x[f.fig4a$x > 12] = f.fig4a$x[f.fig4a$x > 12] + 1
f.fig4a$x[f.fig4a$x > 9] = f.fig4a$x[f.fig4a$x > 9] + 2
f.fig4a$x[f.fig4a$x > 6] = f.fig4a$x[f.fig4a$x > 6] + 1
f.fig4a$x[f.fig4a$x > 3] = f.fig4a$x[f.fig4a$x > 3] + 1
#f.fig4a$x[f.fig4a$x > 18] = f.fig4a$x[f.fig4a$x > 18] + 1
#f.fig4a$x[f.fig4a$x > 12] = f.fig4a$x[f.fig4a$x > 12] + 1
#f.fig4a$x[f.fig4a$x > 6] = f.fig4a$x[f.fig4a$x > 6] + 1
f.fig4a$color = 'steelblue'
f.fig4a$color[f.fig4a$geno == 'A4V'] = 'navy'
f.fig4a$color[f.fig4a$geno == 'silentcha'] = 'limegreen'
f.fig4a$color[f.fig4a$geno == 'A4Vcha'] = 'darkgreen'
f.fig4a$color[f.fig4a$geno == 'silentok'] = 'brown1'
f.fig4a$color[f.fig4a$geno == 'A4Vok'] = 'firebrick'

f.fig4a = f.fig4a[order(f.fig4a$corrected.values),]
f.fig4a = f.fig4a[order(f.fig4a$Sample),]
f.fig4a$x.adj = rep(c(-.25, .25 ,0), 36)

f.fig4a$x = f.fig4a$x + f.fig4a$x.adj

par(mar=c(5.1, 4.1, 4.1, 5.6))

boxplot(f.fig4a$corrected.values~f.fig4a$Sample,
        ##at = c(1:6, 8:13, 15:20, 22:27),
        at = c(1:3, 5:7, 9:11, 14:16, 18:20, 22:24),
        xaxt = 'none',
        xlab = "Day",
        ylab = 'Veloxicty (cm/sec)',
        main = "Female Climbing Velocity")
points(x = f.fig4a$x,
       y = f.fig4a$corrected.values,
       pch = 21,
       bg = f.fig4a$color,
       cex = 1)
axis(side = 1,
     #at = c(3.5, 10.5, 17.5, 24.5),
     at = c(1:3, 5:7, 9:11, 14:16, 18:20, 22:24),
     labels = c(rep("", 18)),
     cex.axis = .5,
     line = 0)

axis(side = 1,
     #at = c(3.5, 10.5, 17.5, 24.5),
     at = c(1:3, 5:7, 9:11, 14:16, 18:20, 22:24),
     labels = c(rep(c(6, 13, 27), 6)),
     cex.axis = .5,
     tick = F,
     line = -.5)

axis(side = 3,
     #at = c(3.5, 10.5, 17.5, 24.5),
     at = c(6, 19),
     labels = c('Silent', 'A4V'),
     cex.axis = 1,
     tick = F,
     line = -.75)

legend('topright',
       inset=c(-0.225,0),
       legend = c('Silent', 'A4V',
                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V',
                  'OK371>gbb;Silent', 'OK371>gbb;A4V'), 
       fill = c('steelblue', 'limegreen', 'brown1',
                'navy', 'darkgreen', 'firebrick'),
       cex = .65,
       bty = 'n',
       pt.cex = .75,
       xpd = T)

abline(v = 12.5, lty = 2, lwd =2)

f.fig4a = fig4ab[grep('f', fig4ab$vial_ID),]
f.fig4a = f.fig4a[f.fig4a$day == 6 |
                  f.fig4a$day == 13 |
                  #f.fig4a$day == 19 |
                  f.fig4a$day == 27,]

f.fig4a$Sample = paste(f.fig4a$geno, f.fig4a$day)
f.fig4a$geno = factor(f.fig4a$geno, levels = c("silent", 'A4V',
                                               'silentcha', 'A4Vcha',
                                               'silentok', 'A4Vok'))

f.fig4a = f.fig4a[order(f.fig4a$day),]
f.fig4a = f.fig4a[order(f.fig4a$geno),]
f.fig4a$Sample = factor(f.fig4a$Sample, levels = unique(f.fig4a$Sample))

f.fig4a = na.omit(f.fig4a)
f.fig4a$x = as.numeric(f.fig4a$Sample)
f.fig4a$x[f.fig4a$x > 15] = f.fig4a$x[f.fig4a$x > 15] + 1
f.fig4a$x[f.fig4a$x > 12] = f.fig4a$x[f.fig4a$x > 12] + 2
f.fig4a$x[f.fig4a$x > 9] = f.fig4a$x[f.fig4a$x > 9] + 1
f.fig4a$x[f.fig4a$x > 6] = f.fig4a$x[f.fig4a$x > 6] + 2
f.fig4a$x[f.fig4a$x > 3] = f.fig4a$x[f.fig4a$x > 3] + 1
#f.fig4a$x[f.fig4a$x > 18] = f.fig4a$x[f.fig4a$x > 18] + 1
#f.fig4a$x[f.fig4a$x > 12] = f.fig4a$x[f.fig4a$x > 12] + 1
#f.fig4a$x[f.fig4a$x > 6] = f.fig4a$x[f.fig4a$x > 6] + 1
f.fig4a$color = 'steelblue'
f.fig4a$color[f.fig4a$geno == 'A4V'] = 'navy'
f.fig4a$color[f.fig4a$geno == 'silentcha'] = 'limegreen'
f.fig4a$color[f.fig4a$geno == 'A4Vcha'] = 'darkgreen'
f.fig4a$color[f.fig4a$geno == 'silentok'] = 'brown1'
f.fig4a$color[f.fig4a$geno == 'A4Vok'] = 'firebrick'

f.fig4a = f.fig4a[order(f.fig4a$corrected.values),]
f.fig4a = f.fig4a[order(f.fig4a$Sample),]
f.fig4a$x.adj = rep(c(-.25, .25 ,0), 36)

f.fig4a$x = f.fig4a$x + f.fig4a$x.adj

par(mar=c(5.1, 4.1, 4.1, 5.6))

boxplot(f.fig4a$corrected.values~f.fig4a$Sample,
        ##at = c(1:6, 8:13, 15:20, 22:27),
        at = c(1:3, 5:7, 10:12, 14:16, 19:21, 23:25),
        xaxt = 'none',
        xlab = "Day",
        ylab = 'Veloxicty (cm/sec)',
        main = "Female Climbing Velocity")
points(x = f.fig4a$x,
       y = f.fig4a$corrected.values,
       pch = 21,
       bg = f.fig4a$color,
       cex = 1)
axis(side = 1,
     #at = c(3.5, 10.5, 17.5, 24.5),
     at = c(1:3, 5:7, 10:12, 14:16, 19:21, 23:25),
     labels = c(rep("", 18)),
     cex.axis = .5,
     line = 0)

axis(side = 1,
     #at = c(3.5, 10.5, 17.5, 24.5),
     at = c(1:3, 5:7, 10:12, 14:16, 19:21, 23:25),
     labels = c(rep(c(6, 13, 27), 6)),
     cex.axis = .75,
     tick = F,
     line = -.5)
axis(side = 1,
     #at = c(3.5, 10.5, 17.5, 24.5),
     at = c(2, 6, 11, 15, 20, 24),
     labels = c(rep(c('Silent', 'A4V'), 3)),
     cex.axis = 1,
     tick = F,
     line = .5)

axis(side = 3,
     #at = c(3.5, 10.5, 17.5, 24.5),
     at = c(4, 13, 22),
     labels = c('Control', 'ChAT>gbb', 'OK371>gbb'),
     cex.axis = 1,
     tick = F,
     line = -.75)

legend('topright',
       inset=c(-0.225,0),
       legend = c('Silent', 'A4V',
                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V',
                  'OK371>gbb;Silent', 'OK371>gbb;A4V'), 
       fill = c('steelblue', 'navy',
                'limegreen', 'darkgreen',
                'brown1', 'firebrick'),
       cex = .65,
       bty = 'n',
       pt.cex = .75,
       xpd = T)

abline(v = c(8.5, 17.5), lty = 2, lwd =2)

@@

@@

male = fig4ab[grep('m', fig4ab$vial_ID),]
male$sample = paste0(male$geno, male$day)

@@

```{r echo = F, fig.width=10}

lcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar=c(5.1, 4.1, 4.1, 15.1))

plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(0, max(c(fmean$mean, mmean$mean))),
     xlim = c(2,27),
     ylab = 'Mean Velocity (cm/s)',
     xlab = 'Day',
     xaxt = 'n',
     main = "Females")

axis(1, at = fmean[fmean$geno == 'silent', 'day'])

lines(x = fmean[fmean$geno == 'silent', 'day'],
      y = fmean[fmean$geno == 'silent', 'mean'],
      type = 'l',
      col = lcol[1],
      lwd = 2)

lines(x = fmean[fmean$geno == 'A4V', 'day'],
      y = fmean[fmean$geno == 'A4V', 'mean'],
      type = 'l',
      col = pcol[2],
      lwd = 2)

lines(x = fmean[fmean$geno == 'silentcha', 'day'],
      y = fmean[fmean$geno == 'silentcha', 'mean'],
      type = 'l',
      col = pcol[3],
      lwd = 2)

lines(x = fmean[fmean$geno == 'A4Vcha', 'day'],
      y = fmean[fmean$geno == 'A4Vcha', 'mean'],
      type = 'l',
      col = pcol[4],
      lwd = 2)

lines(x = fmean[fmean$geno == 'silentok', 'day'],
      y = fmean[fmean$geno == 'silentok', 'mean'],
      type = 'l',
      col = pcol[5],
      lwd = 2)

lines(x = fmean[fmean$geno == 'A4Vok', 'day'],
      y = fmean[fmean$geno == 'A4Vok', 'mean'],
      type = 'l',
      col = pcol[6],
      lwd = 2)

points(x = fmean[fmean$geno == 'silent', 'day'],
       y = fmean[fmean$geno == 'silent', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = fmean[fmean$geno == 'A4V', 'day'],
       y = fmean[fmean$geno == 'A4V', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = fmean[fmean$geno == 'silentcha', 'day'],
       y = fmean[fmean$geno == 'silentcha', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = fmean[fmean$geno == 'A4Vcha', 'day'],
       y = fmean[fmean$geno == 'A4Vcha', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = fmean[fmean$geno == 'silentok', 'day'],
       y = fmean[fmean$geno == 'silentok', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = fmean[fmean$geno == 'A4Vok', 'day'],
       y = fmean[fmean$geno == 'A4Vok', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)

points(x = fmean[fmean$geno == 'silent', 'day'],
       y = fmean[fmean$geno == 'silent', 'mean'],
       bg = hex(pcol[1], .5),
       col = pcol[1],
       pch = 23,
       cex =2)

points(x = fmean[fmean$geno == 'A4V', 'day'],
       y = fmean[fmean$geno == 'A4V', 'mean'],
       bg = hex(pcol[2], .5),
       col = pcol[2],
       pch = 21,
       cex =2)
points(x = fmean[fmean$geno == 'silentcha', 'day'],
       y = fmean[fmean$geno == 'silentcha', 'mean'],
       bg = hex(pcol[3], .5),
       col = pcol[3],
       pch = 23,
       cex =2)
points(x = fmean[fmean$geno == 'A4Vcha', 'day'],
       y = fmean[fmean$geno == 'A4Vcha', 'mean'],
       bg = hex(pcol[4], .5),
       col = pcol[4],
       pch = 21,
       cex =2)
points(x = fmean[fmean$geno == 'silentok', 'day'],
       y = fmean[fmean$geno == 'silentok', 'mean'],
       bg = hex(pcol[5], .5),
       col = pcol[5],
       pch = 23,
       cex =2)
points(x = fmean[fmean$geno == 'A4Vok', 'day'],
       y = fmean[fmean$geno == 'A4Vok', 'mean'],
       bg = hex(pcol[6], .5),
       col = pcol[6],
       pch = 21,
       cex =2)

legend(x = 29,
       y = 1.8,
       legend = c('Silent', 'A4V',
                  'ChAT>gbb;Silent', 'ChAT>gbb;A4V', 
                  'OK371>gbb;Silent', 'OK371>gbb;A4V'),
       pch = c(23,21,23,21,23,21),
       pt.bg = c(hex(pcol[1], .5), hex(pcol[2], .5), hex(pcol[3], .5),
                hex(pcol[4], .5), hex(pcol[5], .5), hex(pcol[6], .5)),
       bty = 'n',
       y.intersp = 1,
       pt.cex = 2,
       xpd=TRUE)

@@

```{r echo = F, fig.width=10}

lcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
pcol = c('steelblue', 'navy', 'limegreen', 'darkgreen', 'brown1', 'firebrick', 'grey')
hex = function(color, alpha){
  rgbvals = col2rgb(color)
  rgb2hex = rgb(rgbvals[1]/255, rgbvals[2]/255, rgbvals[3]/255, alpha)
  return(rgb2hex)
}

par(mar=c(5.1, 4.1, 4.1, 15.1))

plot(x = NA,
      y = NA,
     type = 'n',
     ylim = c(0, max(c(fmean$mean, mmean$mean))),
     xlim = c(2,27),
     ylab = 'Mean Velocity (cm/s)',
     xlab = 'Day',
     xaxt = 'n',
     main = "Males")

axis(1, at = mmean[mmean$geno == 'silent', 'day'])

lines(x = mmean[mmean$geno == 'silent', 'day'],
      y = mmean[mmean$geno == 'silent', 'mean'],
      type = 'l',
      col = lcol[1],
      lwd = 2)

lines(x = mmean[mmean$geno == 'A4V', 'day'],
      y = mmean[mmean$geno == 'A4V', 'mean'],
      type = 'l',
      col = pcol[2],
      lwd = 2)

lines(x = mmean[mmean$geno == 'silentcha', 'day'],
      y = mmean[mmean$geno == 'silentcha', 'mean'],
      type = 'l',
      col = pcol[3],
      lwd = 2)

lines(x = mmean[mmean$geno == 'A4Vcha', 'day'],
      y = mmean[mmean$geno == 'A4Vcha', 'mean'],
      type = 'l',
      col = pcol[4],
      lwd = 2)

lines(x = mmean[mmean$geno == 'silentok', 'day'],
      y = mmean[mmean$geno == 'silentok', 'mean'],
      type = 'l',
      col = pcol[5],
      lwd = 2)

lines(x = mmean[mmean$geno == 'A4Vok', 'day'],
      y = mmean[mmean$geno == 'A4Vok', 'mean'],
      type = 'l',
      col = pcol[6],
      lwd = 2)

points(x = mmean[mmean$geno == 'silent', 'day'],
       y = mmean[mmean$geno == 'silent', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = mmean[mmean$geno == 'A4V', 'day'],
       y = mmean[mmean$geno == 'A4V', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = mmean[mmean$geno == 'silentcha', 'day'],
       y = mmean[mmean$geno == 'silentcha', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = mmean[mmean$geno == 'A4Vcha', 'day'],
       y = mmean[mmean$geno == 'A4Vcha', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)
points(x = mmean[mmean$geno == 'silentok', 'day'],
       y = mmean[mmean$geno == 'silentok', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 23,
       cex =2)
points(x = mmean[mmean$geno == 'A4Vok', 'day'],
       y = mmean[mmean$geno == 'A4Vok', 'mean'],
       bg = 'white',
       col = 'white',
       pch = 21,
       cex =2)

points(x = mmean[mmean$geno == 'silent', 'day'],
       y = mmean[mmean$geno == 'silent', 'mean'],
       bg = hex(pcol[1], .5),
       col = pcol[1],
       pch = 23,
       cex =2)

### 2024-09-27 TKT_RNAseq/R Code/GlycolysisNetwork.Rmd
Dina Folder Update

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
##library(ggpubr)
##library(performance)
library(pathview)
library(visNetwork)
library(org.Dm.eg.db)

>>>>

```{r echo = F, include = F}
library(plotly)
library(org.Dm.eg.db)
##library(ggpubr)
##library(performance)
library(pathview)
library(visNetwork)
